% Please do not change the document class
\documentclass[11pt]{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title+
\title{Continuing Personal Developement Report}


% Please do not change the subtitle
\subtitle{COMP230 - CPD Reports}

% Please put your student number in the author field
\author{1605913}



\begin{document}

\maketitle


\section*{Introduction}

I am still not sure what my specific career goals are at this time, but I feel like I would like to work in Indie development rather than a AAA company, still as I prefer that Jack of all trades nature rather than having a specific job that you are responsible for in AAA. I would also like to try out some self-publishing if I can as at the moment I do not like working within a team, this was because of the BA's having significantly different deadlines to us and thinking that we had the same, this meant we were asked for work that they could do with their free time but we had a boatload of assignments to do plus that. I have enjoyed working in C\# this past year and will find it weird transitioning back to Unreal as that is what my team are using next year, but it's good to learn new languages in my opinion. My five key skills that I need to work on are time management, motivation towards assignments, productiveness, mental health and seeking out new challenges.

\section{Motivation Towards Assignments}
This semester my motivation has been poor but much better than last semesters and I have encountered dips in my motivation, but this was nothing to how awful I felt last semester. The Distributing network task has been the bane of my life this semester and I have had absolutely no desire to work on it, which was similar to the Open GL from last semester I am going to try and fix this by doing little bits of projects at a time and possibly writing down tasks to do for the week that need to be completed before I can do anything "fun" so I don't get behind and gives me some energy to continue doing other projects because I find that if I leave projects for too long or don't understand them I just leave them to the last minute.

\section{Productiveness}
My productivity for my assignments from last semester has improved in my opinion, but this does not mean I have been rushing to finish stuff I have just been trying to complete it to a pass standard or not doing it at all as it seems hopeless. I am hoping by boosting my motivation through doing small tasks that will increase productivity and allow me to do more work compared to this year as I feel like I have gone down from when I was in first year.

\section {Time Management}
My time management has improved in terms of working at my job as I have reduced my hours which has helped amazingly but my time management skills are still so poor that I don't realise how far behind I am everyone else in terms of what they have done and their skill as a programmer and I feel like that is because they plan when they are going to do their projects and this helps them to fit everything in which increases motivation and productivity. This is not as big a problem as Motivation but can still be improved to allow me to do the best work possible.

\section {Programmers Block}
I feel like I have reached a wall at the moment in terms of what I can do as a programmer as nothing I try to learn is really being absorbed it's in one ear and out the other. Which has made me feel like I am behind everyone else and I have not been able to concentrate on assignments as when I do it I think I know what I’m doing but I’ll look at again a while later and it will make no sense. I am going to try to fix this solely concentrating on the work at hand with no distraction, so I can try and retain this info or start writing down what I am doing as I think this will help me to remember what functions do and can be used for.

\section {Seeking Out New Challenges}
I think a way to help myself not feel like I am behind everyone else is to find problems that are challenging and try to solve them instead of going for the easy way out. I just need to do that in my own time now as if I try to do that during assignments I will get stressed and probably have to stop what I am doing and will try to work on something else.

\section*{Conclusion}
In this report, I have identified 5 key skills that I need to work on in the coming semester and how I can improve them. These will hopefully not become burdens for the rest of the semester as I plan on focusing on these problems to improve my work and motivation towards the course.



\bibliographystyle{ieeetran}
\bibliography{References}

\end{document}